\section{Aims and Objectives}
This project is setting out to investigate the considerations that have to be
taken into account in developing an online poker solution, which may not be
present in a real world casino, such as the implementation of a usable GUI, 
a secure random number generator, and secure card picking algorithms. Online 
gambling software has become prevalent in recent years, and developers have to 
be wary of potential pitfalls which can allow malicious actors to exploit the 
computer executed gameplay to their own benefit.

\subsection{Objective 1: A usable GUI}
When playing poker online, the graphical user interface has to be well designed
to convey all the information that is available to the player at a conventional
poker table, whilst being easy to make actions, such as raising the bet to
an arbitrary value. Initial mockups of the GUI will be made, then based on
user acceptance, this initial GUI may be altered to make for a more usable
solution. The usability of the GUI could be measured by asking people to rate
the attributes of the GUI compared to other available poker software's.

\subsection{Objective 2: Secure Pseudo Random Number Generation}
Despite random numbers being easy to access in most programming languages, 
these are in fact not true random numbers, and instead pseudo random numbers, 
which aim to be sufficiently random for real world use, whilst being generated 
by an algorithm. Multiple different random number generation algorithms will
be used, and the cycle lengths and bit size will be examined, to determine if 
a malicious actor can feasibly exploit a repeating of the random numbers or 
low entropy to determine the values of upcoming cards. A GUI application will
be developed to allow dealing of multiple hands, with different random number
sources, and different card picking algorithms, to examine if the spread of
the dealt cards is statistically sufficient.

\subsection{Objective 3: Accurate Gameplay}
As is the main aim of this project, the actual gameplay will have to be
developed to be usable to play poker with. A few different card picking
algorithms will be outlined and compared. High level descriptions of the
client and server's execution will be given, and each step in detail will
then be described, with justifications for individual design choices. The
accuracy of the gameplay can be potentially be validated by creating a test
suite which inputs multiple games into the software, and ensures that the
end result is as expected, e.g.\ each player ends with the correct amount of
chips.
