\section{Aims and Objectives}
This project is setting out to investigate the considerations that have to be
taken into account in developing an online poker solution, which may not be
present in a real world casino, such as the implementation of a usable GUI, 
a secure random number generator, and secure card picking algorithms. Online 
gambling software has become prevalent in recent years, and developers have to 
be wary of potential pitfalls which can allow malicious actors to exploit the 
computer executed gameplay to their own benefit.

\subsection{Objective 1: A Dynamic, Usable GUI}
When playing poker online, the graphical user interface has to be well designed
to convey all the information that is available to the player at a conventional
poker table, whilst being easy to make actions, such as raising the bet to
an arbitrary value. We will look at how to make the GUI dynamic, to adapt to
the players position, and easily resizable, to support multiple types of devices,
and their resolutions.

\subsection{Objective 2: Secure Pseudo Random Number Generation and Fair Shuffles}
Despite random numbers being easy to access in most programming languages, 
these are in fact not true random numbers, and instead pseudo random numbers, 
which aim to be sufficiently random for real world use, whilst being generated 
by an algorithm. Multiple different random number generation algorithms will
be used, and the cycle lengths and bit size will be examined, to determine if 
a malicious actor can feasibly exploit a repeating of the random numbers or 
low entropy to determine the values of upcoming cards. A GUI application has
been developed to allow dealing of multiple hands, with different random number
sources, and different card picking algorithms, to examine if the spread of
the dealt cards is statistically sufficient. 

\subsection{Objective 3: Evaluating Random Number Generation and Shuffles with AI}
An AI is a very valuable tool in the context of poker. It allows users to have
an offline opponent to practice their skills against, but more importantly
allows the software system to be easily tested in an automated way, completing
multiple games in seconds. This allows rare software crashes or incorrect
gameplay to be easily detected without having to manually observe and play
the game thousands of times. Finally, we can use these simple AI's to utilise
automated play to investigate the effect on win percentage incurred by
different shuffling algorithms and random sources.
